CommonMind Consortium: DLPFC

### 2020-09-17 combined_analysis/diff.networks.Rmd
Update diff networks

```{r modules.in.discovery, fig.width=10, fig.height=50}

@@

## Replication cohort
```{r second.cohort, fig.width=6, fig.height=12}
df_cohort2 = df_test[df_test$Cohort == "NIMH-HBCC",]
df_cohort2$Module = factor(df_cohort2$Module, unique(df_cohort2$Module))
table(df_cohort2$FDR < 0.05)

@@

```{r modules.in.second.cohort.Dx, fig.width=15, fig.height=100}

@@

plot_grid( plotlist = figList, ncol=1)
```
<!---

>>>>

```{r modules.in.discovery, fig.width=8, fig.height=50}

@@

## Replication cohort
```{r second.cohort, fig.width=8, fig.height=12}
df_cohort2 = df_test[df_test$Cohort == "NIMH-HBCC",]
df_cohort2$Module = factor(df_cohort2$Module, unique(df_cohort2$Module))
table(df_cohort2$FDR < 0.05)

@@

```{r modules.in.second.cohort.Dx, fig.width=8, fig.height=100}

@@
